\documentclass[../index.tex]{subfiles}

\begin{document}

\clearpage
\chapter*{Abstract}
\addcontentsline{toc}{chapter}{ABSTRACT}

As the application of information and communication technology has become exponentially increased
over the last few years, smart and intelligent devices started to appear in the home environment.
The development of wireless technologies created great freedoms for and more mobility of users with
mobile devices. This also increased the use of mobile devices at home, leading to the birth of
wireless networks in homes. However, the broad adoption of ICT in households created a new security
risks and threats against private assets of users inside the home network. It is becoming more
troublesome as most individuals in the home environment are less skilled and capable to respond
against intruder and hacker attacks. Trojan horse, denial of service, and packet sniffing are
several of many cyber-attacks that can compromise unprotected home computers and devices. Among the
possible measures is to utilize network firewall to establish home network security. Network
firewall provides more security features and network controls over host-based firewall. This project
intends to develop proof-of-concept in establishing home network security by utilizing
enterprise-grade firewall operating system deployed on personal computer. The requirements for the
firewall system will be reviewed in the requirement analysis phase. After the system requirement has
been examined, the project will discuss and define the system design. Afterwards, the initial system
implementation based on the defined design will follow. The system will be tested then according to
the system requirements and objectives before it can be utilized in real environment. The system is
expected to be able to provide proper network security infrastructure for home network environment

\clearpage

\end{document}
