\documentclass[../index.tex]{subfiles}

\begin{document}

\chapter{CONCLUSION}

This chapter will discuss and summarize the achievements and findings gathered from each of project
chapter. Moreover, this chapter will address the advantages and disadvantages of the developed
system. Suggestion for future improvement will be also discussed at the end of the chapter.

\section{Achievement of Project Objectives}

Chapter 1 identified the current issue regarding local area network vulnerability in home
environment. As the guidance for this project, this chapter defined the objectives that should be
fulfilled and project scopes to limit the project development to the defined extent. The project
report organization is also discussed to help with the report writing.

Chapter 2 discussed regarding existing system analysis which focused on examining the current state
of available systems. This stage helped to understand how the existing systems work and identify any
noticeable shortcomings or areas that require improvement.

Chapter 3 reviewed the methodology to be used to develop the system. Following the decision of the
methodology to be used, each of the selected methodology stage is identified and elaborated. This
chapter also addressed system requirement which comprise of hardware and software requirement,
including the role of each requirement in the system development.

Chapter 4 defined the proposed system requirement and design based on Chapter 1, Chapter 2, and
Chapter 3 which includes both functional and non-functional requirement, project design, and
interface design.

Chapter 5 explained the implementation of proposed system by presenting the main system
configuration code. Furthermore, this chapter elaborated the testing stage that has been carried to
check the quality and functionality of the proposed system that comprises of black-box and white-box
testing.

Lastly, Chapter 6 summarized the achievements of preceding chapters, followed by proposed system
advantages compared to existing solutions. This chapter is concluded with several suggestions that
could be reviewed and included in future improvement of the proposed system.


\section{System Advantages}

The proposed system is designed to be an improvement to existing systems. One of the advantages of
this system is the utilization of hypervisor and virtualised environment as the system
infrastructure model. This approach allows multiple guest virtual machines and containers to be
deployed in a single hardware, which is a cost-saving measure for home use.

The components used were selected accordingly to maximize the functionality given with the limited
resource. OPNSense as the primary firewall OS provides user with the ability to configure firewall
rules and utilize Suricata intrusion detection system. The system also employs Pi-hole as DNS server
with DNS sinkhole capability that could filter unwanted content such as advertisement and telemetry.
With these capabilities, Pi-hole could help the system and network to reclaim resource such as
computing power and bandwidth from wasted usage. To monitor all of these subsystems metrics and
behaviors, an LXC container is deployed with the proposed monitoring stack. This monitoring stack
will process metrics and logs of all deployed subsystems and curate it as a centralized dashboard
with essential information.

\section{Suggestion for Future Improvement}

The only faultless system is a system that is never developed. Based on the outcome of the developed
system, there are several suggestions and improvements that could be applied to enhance the system
on fulfilling the requirements further.

Since the beginning of 2023, there are several new mini PC released with decent specification that
could be a good alternative as hardware of this project. One of these devices is Topton i3 N305 fan
less mini PC. This mini PC utilizes low power Intel i3 N305 processor, and 8 cores 8 threads CPU
with only 15W TDP. The use of low power CPU could help on saving electric bill in long term usage.
This mini PC also has 4 Intel i226-V 2.5G RJ45 ports, making it suitable to be used as networking
appliance like this project. Furthermore, the small dimension of this mini PC allows for easy
management and placement.

The firewall usage could also be improved. OPNSense has multiple additional network security plugins
that are available to be installed, such as ZenArmor and CrowdSec. These software have its own
advantages and disadvantages depending on the use case. In future improvement, these software could
be examined and compared to be used with this system as an alternative to the current
implementation.

\end{document}
