\documentclass[../index.tex]{subfiles}

\begin{document}

\chapter{SYSTEM DEVELOPMENT METHODOLOGY}

This chapter defines the development methodology which acts as a guideline to fulfil project's aims
and objectives. The selected methodology will be justified based on how the methodology will help
the development of the project. It will be followed by the explanation of the phases of the selected
methodology. Then, the system requirements will be analysed in order to be able to develop a
reliable system. The chapter will be ended by the conclusion of the previous discussion regarding
the selected methodology, development phases based on the selected methodology, and system
requirement analysis for the project development.

\section{Methodology Selection and Justification}

The primary objective of this project is to successfully develop a hardware firewall which small
business can use to secure their local network. As this project will only involves integration and
configuration of existing software and technology without any application development, the waterfall
model is selected as the development methodology. Waterfall model is selected as the developed
system appliance mainly serve its purpose or function without user-facing interface. This is in
accordance with the definition of waterfall model where the product definition is required to be
stable among the course of the development. Another reason is the project involves hardware
development or configuration where manufacturing or procurement cost are involved. In addition, the
developed system appliance could be considered as critical system which requires extensive safety
and security analysis of the solution specification and design (Balaji \& Murugaiyan, 2012).

\section{Phases of Selected Methodology}

There are five phases which comprises the Waterfall methodology.

\subsection{Requirements Analysis and Definition}

The Waterfall project methodology starts by defining the project requirements. The system services,
constraints, and objectives are established with the system users. They are then defined in detail
and serve as a system specification.

For this system development project, this phase will discuss several network security concerns that
exist in home network environment. After the issues and concerns have been identified, the possible
solution or countermeasures will be discussed. The outcome of the discussion for this phase should
be used as the reference for considerations and justifications in later phases.

\subsection{System Design}

Following the requirements analysis is the system and software design. The system design process
defines the required condition to either software or physical hardware systems. It determines the
entire system architecture in general view.

In this phase, the overall firewall system design will be defined based on the result of requirement
analysis. Both of the hardware and software implementation will be discussed and planned to be
applied in later system development phases

\subsection{Implementation}

The implementation is where the design is accomplished as a set of solution or solution units. This
also includes verification that every implemented unit fulfill its requirements.

When the system development project has reached the Implementation phase, any software and hardware
solutions based on the outcome of Requirement Analysis and System Design phases will be installed
and configured. Initially, the system hardware will be assembled in accordance to the hardware
available or selected by the user. After the hardware have been assembled, the software can start to
be installed and configured based on the requirements


\subsection{Integration and System Testing}

In the integration and system testing phase, the particular solution units or solutions are
implemented and examined as an entire system to guarantee that the project requirements have been
fulfilled. After the system has been thoroughly tested, it will be released to client.

In Integration and System Testing phase, the developed system will be tested based on the defined
testing methodology. This phase will ensure that both the hardware and software aspect of the system
is running properly and provide security to the home network according to the system design.


\subsection{Operation and Maintenance}

After the initial system development, configuration, and testing is done and passed, the system will
be utilized based on the use case. The maintenance stage includes amending the system if in the
later stage there are unintended behaviors that were not found in previous system development phase.

Maintenance involves correcting errors that were not discovered in earlier stages of the life cycle,
improving the implementation of system units, and enhancing the system services as new requirements
are discovered. After the device is deployed and put into use in actual home network, it will be
monitored to analyze its usage and effectiveness in providing network security inside the household.

\section{Technology Used}

To achieve the project objectives defined in previous chapter, the following technology will be
used:

\subsection{Proxmox VE}

Proxmox VE is a type 1 hypervisor which serves as server management platform for enterprise
virtualization. It operates directly on a bare-metal system by utilizing the Linux Containers (LXC)
and KVM hypervisor as well as software-defined networking and storage, all of that implemented on a
single platform.

Proxmox will be used as the appliance's base system. Afterwards, the firewall OS and Pi-hole
container will be deployed on top of it.

\subsection{OPNSense}

OPNsense is an open-source firewall and routing platform based on FreeBSD. A few of its features
including traffic shaping, forward caching proxy, OpenVPN client and intrusion detection system.

OPNsense will be used as the appliance's main OS. It will provide the network- based firewall and
network routing for the local network. A necessary configuration is required to fulfill the
project's objective.

\subsection{LXC}

LXC is one of type 1 hypervisor technology used to run multiple separate Linux system in the form of
container on a control host which utilize single Linux kernel.

LXC is selected to be used for the project as it has minimal overhead compared to other deployment
method. Instead of creating an entire virtual machine, LXC achieves its virtualization by utilizing
virtual environment which has separate network and process space.

In the system development project, LXC will be use for the deployment of Pi- hole application.
Instead of virtualizing the entire operating system only for Pi-hole, LXC can be utilized to provide
the necessary virtualization with noticably lower overhead.

\subsection{Pi-hole}

Pi-hole provides a DNS sinkhole functionality which protects devices connected to the local network
from unwanted content, such as advertisement and internet tracker, without being required to install
any client-side software.

In this project, Pi-hole will be implemented in the system as an advertisement and internet tracker
blocker. Any DNS query will be sent to Pi-hole and Pi-hole will determine if the DNS queries should
be forwarded or allowed or it should be blocked based on the applied rules.

\section{System Requirement Analysis}

To ensure that the developed appliance met the project objectives and deliver its functionality as
optimal as possible, there are several requirements that are required.

\subsection{Hardware Requirement}

The main objective of this project is to develop a low-cost hardware firewall by utilizing an old
PC. As PC is becoming more accessible to every person, it is chosen as the base hardware which the
firewall and additional application will be deployed.

However, to make sure that the appliance will serve its purpose optimally, several specific
requirements are needed.

The main objective of this project is to configure a network-based firewall hosted on a personal
computer (PC). As this project make use of Proxmox and LXC for the virtualization, a decent PC with
multi-cores CPU and high-speed disk are required as to make the system responsive and capable to
fulfill tasks

\subsection{Software Requirement}

For accessing the system through command line interface (CLI), a PC with secure shell (ssh)
capability is required. In Linux environment, the openssh package requires the following
dependencies:

To access the system through web interface, a modern web browser is required. This includes any
recent release of Firefox, Chromium-based browsers, and Safari

\section{Summary}

This chapter discussed the detailed steps for the implementation or developments of the proposed
system. Technologies and system requirement which covers both hardware and software requirements are
defined further. Clearly defining the methodology and system requirements will help to ensure the
project is completed and its objectives and deliverable are achieved within the allocated period.
The system requirement, both software and hardware, also discussed for the purpose of keeping the
system running optimally. This chapter discussed the detailed steps for the implementation or
developments of the proposed system. Technologies and system requirement which covers both hardware
and software requirements are defined further. Clearly defining the methodology and system
requirements will help to ensure the project is completed and its objectives and deliverable are
achieved within the allocated period. The system requirement, both software and hardware, also
discussed for the purpose of keeping the system running optimally.

\end{document}
